RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-03-18 inst/doc/pubs/manuscript.Rmd

* Why NeXML -- because Nexus standard isn't a standard.  Developers extend
it arbitrarily to meet their needs, making it incompatible.  Cannot
represent horizontal gene transfer, ambiguous use of symbols, cannot be
extended reliably, no validator.  NeXML addresses all of these problems
[Vos _et al._ 2012] with a state-of-the-art data management format.

@@

The current stable version of the `RNeXML` package can be installed from
the CRAN library using the standard <!-- Actually not yet -->

@@

There are many promising directions for further development of the
`RNeXML` package.  The project's Milestones page provides a list of
steps currently planned or under consideration.  In particular, these
milestones include increased support for interactive mode of entering data
(wizards), and support for integration of semantics defined through the
Web Ontology language (OWL), as discussed in the Challenges section.

@@

[Temple Lang 2013, XML]: http://cran.r-project.org/web/packages/XML/
[Wickham 2011]: http://vita.had.co.nz/papers/testthat.html
[Chamberlain 2013]: http://dx.doi.org/10.12688/f1000research.2-191.v2
[@ouch]: http://cran.r-project.org/web/packages/ouch/
[@phylobase]: http://cran.r-project.org/web/packages/phylobase
[W3C 2013]: http://www.w3.org/TR/xhtml-rdfa-primer/ "RDFa 1.1 Primer - Second Edition: Rich Structured Data Markup for Web Documents"
[Tenopir et al. 2011]: http://doi.org/10.1371/journal.pone.0021101 "Data Sharing by Scientists: Practices and Perceptions"
[Drew et al 2013]: http://doi.org/10.1371/journal.pbio.1001636

>>>>

* Why NeXML -- because Nexus standard isn't a standard.  Developers extend it arbitrarily to meet their needs, making it incompatible <!-- with? -->.  For example, Nexus cannot represent horizontal gene transfer, ambiguous use of symbols, cannot be extended reliably, and there is no way to validate that it is proper Nexus.  NeXML addresses all of these problems [Vos _et al._ 2012] with a state-of-the-art data management format.

@@

The current stable version of the `RNeXML` package can be installed from
the CRAN library using the standard installation method <!-- Actually not yet -->

@@

There are many promising directions for further development of the
`RNeXML` package.  The project's [Milestones page][milestones] page provides a list of
steps currently planned or under consideration.  In particular, these
milestones include increased support for interactive mode of entering data
(wizards), and support for integration of semantics defined through the
Web Ontology language (OWL), as discussed in the Challenges section.

@@

[Temple Lang 2013, XML]: http://cran.r-project.org/web/packages/XML/
[Wickham 2011]: http://vita.had.co.nz/papers/testthat.html
[Chamberlain 2013]: http://dx.doi.org/10.12688/f1000research.2-191.v2
[@ouch]: http://cran.r-project.org/web/packages/ouch/
[@phylobase]: http://cran.r-project.org/web/packages/phylobase
[W3C 2013]: http://www.w3.org/TR/xhtml-rdfa-primer/ "RDFa 1.1 Primer - Second Edition: Rich Structured Data Markup for Web Documents"
[Tenopir et al. 2011]: http://doi.org/10.1371/journal.pone.0021101 "Data Sharing by Scientists: Practices and Perceptions"
[Drew et al 2013]: http://doi.org/10.1371/journal.pbio.1001636 
[milestones]: https://github.com/ropensci/RNeXML/issues/milestones
